The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Fix reference to Figure 6
Layout

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all logics in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all logics in the \ucoretrack.}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

For the \ucoretrack, we determine the VBS as the best performance in
terms of reduction, i.e., the difference in the number of assertions
of the input formula and the unsat core, within the time limit
of \SI{2400}{s} (the time limit of the \ucoretrack in the competitions
2016--2018).
Figure~\ref{fig:progress-all-app} visualizes VBS performance on the common
benchmarks (\num{91455} total) from 2016--2018 as a bar plot.
For \num{32377} of these benchmarks, extracting an unsat core is trivial since
they contain only one single \texttt{assert} command.
They are thus not considered in the bar plot, since their maximum
possible reduction is trivially 0.

>>>>

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all logics in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all logics in the \ucoretrack.\\${}$}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

For the \ucoretrack, we determine the VBS as the best performance in
terms of reduction, i.e., the difference in the number of assertions
of the input formula and the unsat core, within the time limit
of \SI{2400}{s} (the time limit of the \ucoretrack in the competitions
2016--2018).
Figure~\ref{fig:progress-all-uc} visualizes VBS performance on the common
benchmarks (\num{91455} total) from 2016--2018 as a bar plot.
For \num{32377} of these benchmarks, extracting an unsat core is trivial since
they contain only one single \texttt{assert} command.
They are thus not considered in the bar plot, since their maximum
possible reduction is trivially 0.
